Coherent Hyper-Raman Four Wave Mixing Spectroscopies

### 2024-06-02 paper.tex
add osf statement to paper
Update paper.tex

\graphicspath{{"main/"}}
\begin{document}
%Title of paper
\title{Coherent Hyper-Raman Four Wave Mixing Spectroscopies}

@@

The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
By writing $\vec{\mu} = T_q^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem. \cite{Kowzan2022}
It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
Specifically, it has shown that the rank 1 spherical tensor ($q_1 = -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Andrews1990}
%there is some fancy way to note that theres no index constraint but i dont remember it...
As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$; $\Delta M = 0, \pm1$ transitions are allowed.
This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.

@@

>>>>

\graphicspath{{"figures/"}}
\begin{document}
%Title of paper
\title{Coherent Hyper-Raman Four Wave Mixing Spectroscopies}

@@

The rovibrational selection rules are generated through calculating \autoref{sivebeta} in a $\ket{vJM} \equiv \ket{v} \otimes {\ket{JM}}$ basis, where $\{\ket{v}\}$ is a basis of vibrational states and $\{\ket{JM}\}$ is a basis of rotational states ($J$ is the rotational quantum number and $M$ is its z projection, respectively).
By writing $\vec{\mu} = T_{q_1}^{(1)}$ and $\beta_{ijk} = T_{q_1}^{(1)} + T_{q_2}^{(2)} + T_{q_3}^{(3)}$, where $T^{(k)}_{q}$ is a rank k spherical tensor, it is simple to evaluate the integrals in \autoref{sivebeta} with the Wigner-Eckart theorem. \cite{Kowzan2022}
It is important to note that $\beta_{ijk}$ does not have complete tensor index symmetry.
Specifically, it has shown that the rank one spherical tensor ($T_{q_1}^{(1)}$, with $q_1 \in -1, 0 ,1$) fully contributes to $\beta_{ijk}$ but only select $T_{q_2}^{(2)} + T_{q_3}^{(3)}$ terms contribute. \cite{Andrews1978, Andrews1990}
%there is some fancy way to note that theres no index constraint but i dont remember the language...
As such, its decomposition into irreducible tensor form is allowed only if the values of $q', q''$ are constrained.
By substituting the spherical tensor definitions of $\vec{\mu}$ and $\beta_{ijk}$ into \autoref{sivebeta}, it is clear that only $\Delta J = \pm 1$; $\Delta M = 0, \pm1$ transitions are allowed.
This is expected since $\vec{\mu}$ transitions demand $\Delta J = \pm 1$.
As a result, consistent with vibrational SR-SIVE, rovibrational SR-SIVE follows the same rules as common infrared rovibrational spectroscopy.

@@

\section{Data Availability Statement}
The data and workup scripts that support this study are permissively licensed and available for reuse at https://osf.io/2amkq/.
